Supplementary Material \\ \large{Heterogenous firing responses leads to diverse coupling to presynaptic activity in a simplified morphological model of layer V pyramidal neurons}

### 2016-06-19 derivation_supplementary/supplementary.tex
up supp

% Created 2016-06-19 Sun 00:51
\documentclass[colorlinks]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{fixltx2e}
\usepackage{graphicx}
\usepackage{longtable}
\usepackage{float}
\usepackage{wrapfig}
\usepackage{rotating}
\usepackage[normalem]{ulem}
\usepackage{amsmath}
\usepackage{textcomp}
\usepackage{marvosym}
\usepackage{wasysym}
\usepackage{amssymb}
\usepackage{hyperref}
\tolerance=1000
\hypersetup{allcolors = blue} % to have all the hyperlinks in 1 color
\renewcommand{\refname}{\vspace{-.8cm}}
\usepackage{jneurosci}
\bibliographystyle{jneurosci}
\author{Y. Zerlaut \& A. Destexhe}
\date{\today}
\title{Supplementary Material \\ \large{Heterogenous firing responses leads to diverse coupling to presynaptic activity in a simplified morphological model of layer V pyramidal neurons}}
\hypersetup{
  pdfkeywords={},
  pdfsubject={},
  pdfcreator={Emacs 24.5.1 (Org mode 8.2.10)}}
\begin{document}

@@

\begin{equation}
\lambda^p= \sqrt{\frac{r_m}{r_i (1 + r_m g_{e0}^p + r_m g_{i0}^p)}}
\quad 
\lambda^d= \sqrt{\frac{r_m}{r_i (1 + r_m g_{e0}^d + r_m g_{i0}^d)}}$
\end{equation}

@@

Now used distribution theory (see \citetext{Appel2008} for a
comprehensive textbook) to translate the synaptic input into boundary
conditions at $X_{src}$, physically this corresponds to: 1) the
continuity of the membrane potential and 2) the discontinuity of the
current resulting from the synaptic input.

@@

\item \$ L$_{\text{p}}$ $\le$ X$_{\text{src}}$\$
\label{sec-3-0-0-2}

@@

\begin{equation}
K_f(X_{src}) = 
\left\{
\begin{split}
& A_f(X_{src}) \forall X_{src} \in [0,L_p] \\
& E_f(X_{src}) \forall X_{src} \in [L_p, L]
\end{split}
\right.
\end{equation}
\end{enumerate}

\section{Deriving the fluctuations properties}
\label{sec-4}

From shotnoise theory \cite{Daley2007} (see also
\citetext{ElBoustani2009a} for an application similar to ours), we can
obtain the power spectral density of the V$_{\text{m}}$ fluctuations \( P_V(f) \)
as a response to the stimulation Equation \texttt{eq:fluct-eq}:

\begin{equation}
\label{eq:vm-pwd}
 P_V(f)  = & \sum_{syn} \pi \mathcal{D}_{syn}  \nu_{syn} \, \| \hat{\mathrm{PSP}}(f) \|^2 
\end{split}
\end{equation}

@@

\section{References}
\label{sec-5}
\bibliography{biblio}
% Emacs 24.5.1 (Org mode 8.2.10)
\end{document}

>>>>

% Created 2016-06-19 Sun 00:51
\documentclass[colorlinks]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{amsmath, amssymb}
\usepackage{hyperref}
%% \tolerance=1000
\hypersetup{allcolors = blue} % to have all the hyperlinks in 1 color
\renewcommand{\refname}{\vspace{-.8cm}}
\usepackage{jneurosci}
\bibliographystyle{jneurosci}
\author{Y. Zerlaut \& A. Destexhe}
\date{\today}
\title{Supplementary Material \\ \large{Heterogenous firing responses leads to diverse coupling to presynaptic activity in a simplified morphological model of layer V pyramidal neurons}}
\begin{document}

@@

\begin{equation}
\lambda^p= \sqrt{\frac{r_m}{r_i (1 + r_m g_{e0}^p + r_m g_{i0}^p)}}
\quad 
\lambda^d= \sqrt{\frac{r_m}{r_i (1 + r_m g_{e0}^d + r_m g_{i0}^d)}}
\end{equation}

@@

We now use distribution theory (see \citetext{Appel2008} for a
comprehensive textbook) to translate the synaptic input into boundary
conditions at $X_{src}$, physically this corresponds to: 1) the
continuity of the membrane potential and 2) the discontinuity of the
current resulting from the synaptic input.

@@

\item $ L_p \le X_{\text{src}}$
\label{sec-3-0-0-2}

@@

\begin{equation}
K_f(X_{src}) = 
\left\{
\begin{split}
& A_f(X_{src}) \quad \forall X_{src} \in [0,L_p] \\
& E_f(X_{src}) \quad \forall X_{src} \in [L_p, L]
\end{split}
\right.
\end{equation}
\end{enumerate}

\section{Deriving the power spectrum of the membrane potential fluctuations}
\label{sec-4}

The calculus rely on the ability to obtain the power spectrum of the
membrane potential fluctuations at the soma $P_V(f)$.

This can be obtained from shotnoise theory \cite{Daley2007} (see also
\citetext{ElBoustani2009a} for an application similar to ours), the
general form can be expressed as:

\begin{equation}
\label{eq:vm-pwd}
P_V(f)  = \sum_{\{syn\}} N_{syn} \,  F_\mathrm{synch} \, \nu_{syn}
\, \| \hat{\mathrm{PSP}_{syn}}(f) \|^2 
\end{split}
\end{equation}

where $\{syn\}$ is the set of identical synapses, each having
$N_{syn}$ synapses, a Poisson release probability: $\nu_{syn}$ and
creating a post-synaptic event $\mathrm{PSP}_{syn}(t)$.

In addition, we added a synchrony factor $F_\mathrm{synch}$ that
accounts for the effects of the synchronous arrivals of presynaptic
events. Given the synchrony generator considered in the main text, the
synchrony factor takes the form:

\begin{equation}
\label{eq:F-synch}
F_\mathrm{synch} =(1-s) + (s-s^2) 2^2 + (s^2-s^3) 3^2 + s^3 4^2
\end{split}
\end{equation}

because single events arise with a probability $1-s$, double events
with a probability $s-s^2$ (and the PSP are squared in
Eq. \ref{eq:vm-pwd}, hence the $2^2$ factor), etc...

\section{Deriving the fluctuations properties}
\label{sec-5}

@@

\section{References}
\label{sec-5}
\bibliography{biblio}

\end{document}
